\centering Syscoin 4.0: A Peer-to-Peer Electronic Cash System Built For Business Applications

### 2021-05-21 syscoin_4.0/article.tex
MDPI submission
wp edits

High gas fees and low transaction throughput are some of the key issues that are hindering ERC-20 projects from running at scale. However, Ethereum 2.0 is currently under development to address these issues, where its final release is anticipated to be completed several years from now \ref{But19}. Instead of building a competing smart contract system, we have decided to work with the EVM protocol, and to provide a faster and cost effective alternative to what Ethereum 2.0 is proposing. The roadmap for Syscoin 4.0 proposes a four-layer tech stack to address this using: (a) Syscoin as the base layer to provide security; (b) EVM for programmability; (c) ZKP for scalability; and (d) applications to provide decentralized usability for the next phase of the Internet's evolution, known as Web 3.0.

In Section \ref{sec:protocol} we address the protocol attributes, which include ZDAG, order-of-events, point-of-sale applications, assets, non-fungible tokens, lightning networks, offers/escrow, and masternodes. In Section \ref{section:roadmap} we lay out the roadmap for Syscoin 4.0, which includes scalability, design proposal, evidence, and applications. In Section \ref{section:specs} we outline the protocol specifications, followed by the conclusion in Section \ref{section:conclusion}.

@@

\subsection{Z-DAG}
Z-DAG (Zero-Confirmation Directed Acyclic Graph) is an instant settlement protocol functioning across all Syscoin services. Syscoin services consist of Alias Identities, Certificates, Escrow, Offers and Assets.
Each service is controlled via an Alias, in which ownership is proven through a private key that matches each
unique address. Z-DAG organizes transactions based on dependencies to build the state in a deterministic fashion. This helps protect against double spends where an Asset is transferred falsely by creating multiple transactions through multiple nodes within a short time.

@@

Figure \ref{fig:current_vs_zdag}  shows the difference between a regular blockchain and Syscoin’s Z-DAG implementation. Syscoin now has two consensus layers: In the first layer, a Z-DAG graph of transactions are represented in the mempool without a block, providing settlement in real-time. The secondary layer provides confirmation and conflict resolution preventing double-spend events through existing Proof of Work (PoW) consensus.

Verifying client nodes creates a graph of transactions by looking at the sender/receiver list of Asset transfers. A
circuit detection algorithm is applied (read below Hawick cycle detection) and used to remove cycles from within the graph to create a DAG (Directed Acyclic Graph). Once the DAG is created it is topologically sorted with an asset transfer consensus code being processed in sequence, to form a deterministic state among the entire network in consensus.

@@

A User Interface layer will notify the user of conflicts in real-time, making the transaction occur between 3-5
seconds (ie, the amount of time needed to ensure that network takes to notice that 2 double spend transactions are conflicting with each other). This is possible through Syscoin’s Masternode layer. Every Masternode is connected to 25 or more peers providing high-throughput relay across the network, averaging one or more network hops to transmit from the sender to the receiver nodes.

The partition tolerance of the protocol is the PoW block timing which is set to 60 seconds on Syscoin 3. For every block, a new DAG is constructed from the transactions within that block. Unlike other implementations that have no PoW to fall back on, there is no case where the DAG tends toward an incorrect state over time.To accurately detect double-spends, other implementations such as Phantom or Spectre \ref{Som15} must use an algorithm to replace the longest chain rule to derive the order of events and attacker sequences in a graph.
These implementations end up in a more complex game theoretical situation that has not mathematically been proven to be accurate in all cases. Syscoin relies on the thoroughly tested Nakamoto consensus model to arrive at a consensus over time rather than simply relying on a DAG.

@@

\subsection{CAP Theorem}
The CAP theorem \ref{Bre12} states that it is impossible for a distributed data store to simultaneously provide more than two out of the following three guarantees: consistency, availability or partition tolerance. Bitcoin attempts to provide a guarantee that transactions are settled, but is not able to do so according to theory. Z-DAG trades some consistency for some availability. Since it is unlikely that a double-spend or re-organization will change the state of someone’s balance, we do not wait for settlement finality by waiting for blocks to confirm. This drastically increases the usability in pointof-sale applications.

@@

Sed lectus. Integer euismod lacus luctus magna. Quisque cursus, metus vitae pharetra auctor, sem massa mattis sem, at interdum magna augue eget diam. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Morbi lacinia molestie dui. Praesent blandit dolor. Sed non quam. In vel mi sit amet augue congue elementum. Morbi in ipsum sit amet pede facilisis laoreet. Donec lacus nunc, viverra nec, blandit vel, egestas et, augue. Vestibulum tincidunt malesuada tellus. Ut ultrices ultrices enim. Curabitur sit amet mauris.

@@

With a subset of nodes offering sybil resistance through the requirement of bonding 100,000 SYS to become active, plus the upcoming deterministic masternode feature in Syscoin 4.2, we have enabled Chain Locks which attempts to solve a long-standing security problem in Bitcoin \cite{Eya18}, where Dashcore was the first project to implement this idea \cite{Blo18} which the industry has since widely accepted as a viable solution \cite{Val19}. Our implementation is an optimized version of this, in that we do not implement Instant Send or Private Send transactions and thus Syscoin’s Chain Lock implementation is much simpler. Because of merged-mining functionality with Bitcoin, we believe our chain coupled with Chain Locks becomes more secure via solving Bitcoin’s most vulnerable attack vector (ie, selfish mining).

@@

With 2400+ masternodes running fullnodes, Z-DAG becomes more dependable, as does the propagation of blocks and potential forks. Masternodes are bonded through a loss-less strategy of putting 100,000 Syscoin in an output and running full nodes in exchange for block rewards. A seniority model incentivizes masternodes to share long-term growth by paying more for the longer period of service. Half of the transaction fees are also shared between the PoW miners and masternodes to ensure long term alignment once subsidy becomes negligible. Coins are not locked at any point, and there is no slashing condition if masternodes decide to move their coins, the rewards to those masternodes simply stop. Sharing Bitcoin’s compact block design, it consumes very little bandwidth to propagate blocks assuming the memory pool of all these nodes is roughly synchronized \cite{BitCore}. The traffic on the network primarily consists of propagating the missing transactions to validate these blocks. Having a baseline for a large number of full-nodes that are paid to be running allows us to create a very secure environment for users. It proposes higher costs to would-be attackers who either have to attempt a 51\% attack of Syscoin (effectively also trying to attack the Bitcoin network), or try to game the mesh network by propagating bad information which is made more difficult by incentivized full-nodes. The health of a decentralized network consists of the following; (a) the mining component or consensus to produce blocks, and (b) the network topology to disseminate information in a timely manner in conditions where adversaries might be lurking. Other attacks related to race conditions in networking or consensus code are mostly negligible as Syscoin follows a rigorous and thorough continuous development process. This includes deterministic builds, Fuzz tests, ASAN/MSAN/TSAN, functional/unit tests, multiple clients and adequate code coverage. Syscoin and Bitcoin protocol code bases are merged daily such that the build/signing/test processes are all identical, allowing us to leverage the massive developer base of Bitcoin. The quality of code is reflective of taking worst case situations into account. The most critical engineers and IT specialists need confidence that value is secure should they decide to move their business to that infrastructure. It’s true that there are numerous new ideas, new consensus protocols and mechanisms for achieving synchronization among users in a system through light/full node implementations. However, in our experience in the blockchain industry over the last eight years, we understand that it takes years, sometimes generations to bring those functionalities to production level quality useful for commercial applications.

@@

Bitcoin was the first to offer a practical outcome in the General's Dilemma using Crypto Economic rationale and incentives. Ethereum was the first to abstract the concept of turing completeness within similar frameworks assumed by Bitcoin. What Syscoin presents is a combination of both Bitcoin and Ethereum with intuitions built on top to achieve a more efficient financial computing platform which leverages coordination to achieve consensus using Crypto Economic rationale and incentives. We propose a four-layer tech stack using Syscoin as the base (host) layer, which provides an efficient (ie, low gas cost per transaction) platform. Some of the main advantages include building scalable decentralized applications, the introduction of a decentralized cost model around Ethereum Gas fees. This new model proposes state-less parallelized execution and verification models while taking advantage of the security offered by the Bitcoin protocol. We may also refer to this as Web 3.0.

@@

Put in context, even Lightning Networks for transactional counts qualifies as a form of sublinear scaling on a transactional basis but not per user, as users must necessarily enter the main chain first before entering a payment channel. It requires the state of the blockchain to include users joining the system. This state (ie, UTXO balances) is the primary  factor of efficiency degradation in Bitcoin. Users need to first start on the main chain and then move into the payment channel system to receive money, meaning that scale is at best O(N) where N is the number of users. There are some solutions to this problem of state storage on Bitcoin by reducing it via an alternative accumulator strategy to the cost of increased bandwidth \cite{Dry19}. This approach would make the chain state-less,  however the validation costs would remain linear to the number of transactions being done. When combined with payment channels, only the costs to get in/out are factored into the validation. This offers an interesting design for payments themselves while providing for on-chain availability. We consider this as a satisfactory path for futuristic scalable payments. Hence, it is not possible to employ that strategy with general computations. With this design, we are still left with the issue on how to do general computations at higher efficiency.

@@

While many compelling arguments can be made migrating to a state-less design \cite{Hot19}, it is not possible to achieve sublinear efficiency without sacrificing some other desired component as outlined above. To achieve polylogarithmic efficiency, it is necessary to have a mix of state and stateless nodes working together in harmony on a shared ledger \cite{Hot19}. This should be accomplished so that business processes can dictate direction, and users can choose to pay a little more for security either by using a stateful yet very scalable ledgering mechanism or by paying to ensure their own data availability amortized over the life of that user on such systems. Presenting the ability for users to make these choices allows us to separate the consensus of such systems and reduce overall complexity. However, in whatever solution we adopt, we need to ensure that the final implementation allows for both the liveness and safety of that state, which are defined as follows:

@@

Hardware enclaves (eg, Intel SGX through remote attestation) were also of particular interest to the Syscoin team as a way to offload execution and avoid re-execution costs. However, there are a myriad of attack vectors and censorship concerns on the Intel platform. We also should note that the Antarctica model was interesting but required a firmware update from Intel to support such a feature which raises concerns over censorship long term \cite{Nil20}.

The theme amongst all of these approaches is that although re-execution is avoided the communication complexity is largely still linear with the number of transactions on the main chain. The security and trust models are also different from that of the layer 1 assumptions which was not desired.

@@

ZKP allows for the desired superlinear scaling trait we had been looking to achieve, but also offer other benefits; namely privacy is very easy to introduce and will not add detectable costs and complexities to verification on the mainchain. With users controlling their own data, the mainchain and systems may be designed such that only balance adjustments are recorded, not transaction sets (we will explain the case with full data availability below). In this scenario, there is no advantage for a miner to gain when to collude with users to launch attacks on systems such as Decentralize Finance (DeFi) pools and provenance of transactions. The flexibility has to be present for application developers that need experiences consistent with those we have today with Bitcoin/Syscoin/Ethereum. This would enable the privacy use-cases without requiring extra work, knowledge or costs.

@@

Hashing with the SHA256 algorithm is regarded to be quantum safe because it requires Grover's algorithm to crack in the post-quantum world, and at best the quantum computer will offer only 50\% reduction in time to break \cite{Nai19}. On the other hand, where Shor’s algorithm applies, any pair based cryptographic system will be broken in hours.

@@

\begin{figure}[h!]
\includegraphics[width=3.7in]{img/4_layer.png}
\label{fig:tech_stack}
\caption{Proposed 4-layer tech stack for Syscoin} 
\end{figure}

@@

As seen in Figure 6, work done on BTC is reused to create SYS blocks through the merged-mining specification. Concurrently, the miner will execute smart contracts in the memory pool of the node running the EVM chain. Once a chain hash has been established post-execution, it will be put into the coinbase of the Syscoin block and published to the network. Upon receiving these blocks, every node would verify that the EVM chain, which can be locally executed (ie, similar to the miner), matches the state described by the Syscoin block. Technically, one would want to ensure both the latest and previous EVM block hashes inside of their respective Syscoin blocks are valid. The block $->$ evmblock $==$ evmblock \&\& block $->$ prev $==$ evmblock $->$ prev is all that is needed to link the chains together with work done by Bitcoin which is propagated to Syscoin through AUXPOW and can serve as a secure ledgering mechanism for the EVM chain.

Since (a) we may use eWASM; (b) there are paid full nodes running on the network; and (c) the mining costs are shared with Bitcoin miners, we should be able to safely increase the amount of bandwidth available in the EVM chain while remaining secure from large uncle orphan rates. There has been much discussion as to what the safe block size should be on Ethereum. Gas limits are increasing as optimizations are made on the Ethereum network. However, since this network would be ledgered by the Syscoin chain through PoW, there shouldbe no concern for uncle orphaning of blocks since the blocks must adhere to the policy set inside of the Syscoin block. We should therefore be able to increase bandwidth significantly and parameterize for a system that will scale globally yet still be centered around L2 rollup designs. A very important distinction to note is that the design of Ethereum 2.0 centers around a Beacon chain and sharding served by a Casper consensus algorithm \cite{But17}. The needs of the algorithm require a set of finality guarantees necessitating a move towards Proof-of-Stake (PoS). This has large security implications for which we may not have formal analysis for a long time, however we do know it comes with big risk \cite{Neu21}.  We offer similar levels of scalability on a network while retaining Nakamoto Consensus security. The simpler design which has been market tested and academically verified to work would result in a more efficient system as a whole with less unknown and undocumented attack vectors. The only research that would need to be made therefore is on the optimal parameterization of the gas limit taking into account an L2 centric system but also a safe number of users we expect to be able to serve before fee market mechanisms begin to regulate the barrier of entry for these users. This proposed system should be scalable enough to serve the needs of global generalized computation while sticking to the core fundamentals set forth in the design ideals above. Our upcoming whitepaper will have more analysis on these numbers but we will include some theoretical scaling metrics at the end of this article.

@@

Aleo uses Zero knowledge EXEcution (Zexe) for zkSNARK proof creation through circuits created from R1CS constraints. The interesting thing about Aleo is that there is a ledger itself that is purpose-built to only verify these Zexe proofs for privacy preserving transactability. The consensus is PoW, while the proof system involves optimizing over the ability to calculate the verifications of these proofs efficiently. The more efficient these miners become at verifying these proofs, the faster they are able to mine and thus the system provides sybil resistance through providing resources to verify Zexe proofs as a service in exchange for block creation. However, these proof creations can be done in parallel based on the business logic for the systems the developers need to create. There is no direct need for on-chain custom verification as these can be done in an EVM contract, similar to what Cairo Generic Proving Service (GPS) verifier and Zinc Verification do. The goal of Aleo is to incentivize miners to create specialized hardware to more efficiently mine blocks with verification proofs. However, provers can also do this as we have seen with Matter Labs’ recent release of FPGA to do more efficient zkSNARK proofs \cite{Glu20}. It is a desirable property to use PoW to achieve “world-view” consensus in Aleo; however they focus on private transactions. They are typically not batched and employ a recursive outer proof to guarantee execution of an inner proof where the outer proof is sent to the blockchain to be verified. This proof is a limited 2-step recursion, consequently batching of arbitrary amounts of transactions is not supported. However, as a result the cost of proof verification is relatively constant with a trade-off of limiting the recursion depth. Aleo is not meant to be a scalable aggregator of transactions, but mainly oriented towards privacy in their zk-SNARK constructions using Zexe.

@@

An EVM layer will support general smart contracts compatible with existing Ethereum infrastructure and L2 rollups will enable massive scale. The different types of zkRollups will allowbusinesses and rollup providers to offer ability for custom fee markets (ie, pay for fees in tokens other than base layer token SYS). In addition, it will remove costs and thus improve scale of systems by offering custom data availability consensus modules. This design discussed here shares similarities to the zkPorter design where a smart contract would sign off on data availability checks that would get put into the ZKP as part of the validity of a zkBlock which goes on chain.

@@

This concludes that shards can define different consensus modules for data availability (censorship resistance mechanisms) via separating concerns around ledgering the world-view of the state (ie, ZKP that is put on L1 and the data that represents the state. Doing so would allow shards to increase scale, offload costs of data availability to consensus participants.

@@

Since payment channels work with UTXO’s and also benefit from on-chain scaling via Z-DAG, 16MB blocks (with segwit weight) assumed, we will see somewhere around 8MB-12MB effectively per minute (per block). We foresee that is sufficient to serve Seven Billion people who may enter and exit the payment channel networks once a year (ie, 2 transactions on chain per person per year) for a total of 14 Billion transactions. Let’s conservatively assume 8MB blocks and 300 bytes per transaction. Once on a payment channel, the number of transactions is not limited to on-chain bandwidth, but to network related latencies and bandwidth costs. Therefore, we will conclude that our payment scalability will be able to serve billions of people doing 2 on-chain transactions per year which is arguably realistic based on the way we envision payments to unfold; whether that is an L2 or payment channel network that will hold users to pay through instant transaction mechanisms. On-chain, we have some metrics on Z-DAG throughput [1]; in those cases someone needs to transact for point-of-sale using the Syscoin chain. The solution for payments ends up looking like a hybrid mechanism of on-chain (Z-DAG) and off-chain (ie, payment channel) style payments.

@@

\subsubsection{Gas Costs}

Starkware was able to process 300k transactions over 8 blocks with a total cost of 94.5M gas; final throughput was 3000 TPS (see Reddit bake-off estimates). As a result, or the following calculations, let’s assume one batch-run to be 300k transactions.
Ethereum can process ~200kB of data per minute, with a cost limit of 50M gas per minute. Therefore, considering the Starkware benchmark test, and assuming a block interval of 13 seconds, we would achieve ~ 3000 TPS (ie,  300 k transactions per batch-run / (8 blocks per batch-run * 13 seconds per block))

@@

With regards to the SYSX cost estimates; simulated gas costs were generated using Ethereum's proposed EIP 1559 (Figure \ref{fig:sysx_gas_costs_eip_1559}) and an alternative pricing mechanism that Syscoin is currently exploring (Figure \ref{fig:sysx_gas_costs_m1}). This alternative approach is called the BLock Occupancy Cost (BLOC) function (\ref{fig:bloc}), and is driven by the occupancy of the previously generated block; see Figure \ref{fig:blk_occupancy_simulations} for simulations Appendix D for details.

@@

\section{EIP 1559}

>>>>

High gas fees and low transaction throughput are some of the key issues that are hindering ERC-20 projects from running at scale. However, Ethereum 2.0 is currently under development to address these issues, where its final release is anticipated to be completed several years from now \cite{But19}. Instead of building a competing smart contract system, we have decided to work with the EVM protocol, and to provide a faster cost effective alternative over Ethereum 2.0. The roadmap for Syscoin 4.0 proposes a four-layer tech stack to address this using: (a) Syscoin as the base layer to provide security; (b) EVM for programmability; (c) ZKP for scalability; and (d) applications to provide decentralized usability for the next phase of the Internet's evolution, known as Web 3.0.

In Section \ref{sec:protocol} we address the protocol attributes, which include Z-DAG, order-of-events, point-of-sale applications, assets, non-fungible tokens, lightning networks, offers/escrow, and masternodes. In Section \ref{section:roadmap} we lay out the roadmap for Syscoin 4.0, which includes scalability, design proposal, evidence, and applications. In Section \ref{section:specs} we outline the protocol specifications, followed by the conclusion in Section \ref{section:summary}.

@@

\subsection{Z-DAG}
Zero-Confirmation Directed Acyclic Graph (Z-DAG) is an instant settlement protocol functioning across all Syscoin services. Syscoin services consist of Alias Identities, Certificates, Escrow, Offers and Assets. Each service is controlled via an Alias, in which ownership is proven through a private key that matches each
unique address. Z-DAG organizes transactions based on dependencies to build the state in a deterministic fashion. This helps protect against double spends where an asset is transferred falsely by creating multiple transactions through multiple nodes within a short time.

@@

Figure \ref{fig:current_vs_zdag}  shows the difference between a regular blockchain and Syscoin’s Z-DAG implementation. Syscoin now has two consensus layers. The first layer consists of a Z-DAG graph of transactions are represented in the mempool without a block, providing settlement in real-time. The secondary layer provides confirmation and conflict resolution preventing double-spend events through existing Proof-of-Work (PoW) consensus.

Verifying client nodes creates a graph of transactions by looking at the sender/receiver list of asset transfers. A circuit detection algorithm is applied (read below Hawick cycle detection) and used to remove cycles from within the graph to create a DAG (Directed Acyclic Graph). Once the DAG is created, it is topologically sorted with an asset transfer consensus code processed in sequence, to form a deterministic state among the entire network in consensus.

@@

A User Interface (UI) layer will notify the user of conflicts in real-time, making the transaction occur between 3-5 seconds (ie, the amount of time needed to ensure that network takes to notice that 2 double spend transactions are conflicting with each other). This is possible through Syscoin’s Masternode layer. Every Masternode is connected to 25 or more peers providing high-throughput relay across the network, averaging one or more network hops to transmit from the sender to the receiver nodes.

The partition tolerance of the protocol is the PoW block timing, which is set to 60 seconds on Syscoin 3. For every block, a new DAG is constructed from the transactions within that block. Unlike other implementations that have no PoW to fall back on, there is no case where the DAG tends toward an incorrect state over time. To accurately detect double-spends, other implementations such as Phantom or Spectre \cite{Som15} must use an algorithm to replace the longest chain rule to derive the order of events and attacker sequences in a graph.
These implementations end up in a more complex game theoretical situation that has not  been proven mathematically to be accurate in all cases. Syscoin relies on the thoroughly tested Nakamoto consensus model to arrive at a consensus over time rather than simply relying on a DAG.

@@

\subsection{CAP Theorem}
The CAP theorem \cite{Bre12} states that it is impossible for a distributed data store to simultaneously provide more than two out of the following three guarantees: consistency, availability or partition tolerance. Bitcoin attempts to provide a guarantee that transactions are settled, but is not able to do so according to theory. Z-DAG partially trades consistency for availability. Since it is unlikely that a double-spend or re-organization will change the state of someone’s balance, we do not wait for settlement finality by waiting for blocks to confirm. This drastically increases the usability in point-of-sale applications.

@@

Non-Fungible Tokens (NFTs) are unique Syscoin-based digital assets that can not be replaced with something else. Some example uses are: (a) gaming; (b) digital art; (c) physical assets; and (d) digital collectibles. Some advantages of using Syscoin over other platforms include scalability, divisibility, efficiency, and notary capabilities.

By utilizing the NEVM, Syscoin will offer NFTs running off the application layer of its tech-stack which will offer a competitive advantage over Ethereum in terms of scalability. Another interesting feature Syscoin will be offering is divisibility. A good example of this is land ownership where fractions of such assets can be apportioned between multiple parties. Finally, developers will be able to employ notary capabilities by applying custom rule sets to transactions involving NFTs.

@@

With a subset of nodes offering sybil resistance through the requirement of bonding 100,000 SYS to become active, plus the upcoming deterministic masternode feature in Syscoin 4.2. We have enabled Chain Locks which attempts to solve a long-standing security problem in Bitcoin \cite{Eya18}. Dashcore was the first project to implement this idea \cite{Blo18} which the industry has since widely accepted as a viable solution \cite{Val19}. Our implementation is an optimized version of this, in that we do not implement Instant Send or Private Send transactions and thus Syscoin’s Chain Lock implementation is much simpler. Because of merged-mining functionality with Bitcoin, we believe our chain coupled with Chain Locks becomes more secure via solving Bitcoin’s most vulnerable attack vector (ie, selfish mining).

@@

With 2400+ masternodes running fullnodes, Z-DAG becomes more dependable, as does the propagation of blocks and potential forks. Masternodes are bonded through a loss-less strategy of putting 100,000 Syscoin in an output and running full nodes in exchange for block rewards. A seniority model incentivizes masternodes to share long-term growth by paying more for the longer period of service. Half of the transaction fees are also shared between the PoW miners and masternodes to ensure long term alignment once subsidy becomes negligible. Coins are not locked at any point, and there is no slashing condition if masternodes decide to move their coins, the rewards to those masternodes simply stop. Sharing Bitcoin’s compact block design, it consumes very little bandwidth to propagate blocks assuming the memory pool of all these nodes is roughly synchronized \cite{BitCore}. The traffic on the network primarily consists of propagating the missing transactions to validate these blocks. Having a baseline for a large number of full-nodes that are paid to be running allows us to create a very secure environment for users. It proposes higher costs to would-be attackers who either have to attempt a 51\% attack of Syscoin (ie, effectively trying to attack the Bitcoin network), or try to game the mesh network by propagating bad information which is made more difficult by incentivized full-nodes. The health of a decentralized network consists of the following; (a) the mining component or consensus to produce blocks, and (b) the network topology to disseminate information in a timely manner in conditions where adversaries might be lurking. Other attacks related to race conditions in networking or consensus code are mostly negligible as Syscoin follows a rigorous and thorough continuous development process. This includes deterministic builds, Fuzz tests, ASAN/MSAN/TSAN, functional/unit tests, multiple clients and adequate code coverage. Syscoin and Bitcoin protocol code bases are merged daily such that the build/signing/test processes are all identical, allowing us to leverage the massive developer base of Bitcoin.  Code quality is reflective of taking worst case situations into account. The most critical engineers and IT specialists need confidence that value is secure should they decide to move their business to that infrastructure. It’s true that there are numerous new ideas, new consensus protocols and mechanisms for achieving synchronization among users in a system through light/full node implementations. However, in our experience in the blockchain industry over the last eight years, we understand that it takes years, sometimes generations to bring those functionalities to production level quality useful for commercial applications.

@@

Bitcoin was the first to offer a practical outcome to the General's Dilemma using Crypto Economic rationale and incentives. Ethereum was the first to abstract the concept of turing completeness within similar frameworks assumed by Bitcoin. What Syscoin presents is a combination of both Bitcoin and Ethereum with intuitions built on top to achieve a more efficient financial computing platform which leverages coordination to achieve consensus using Crypto Economic rationale and incentives. We propose a four-layer tech stack using Syscoin as the base (host) layer, which provides an efficient (ie, low gas cost per transaction) platform. Some of the main advantages include building scalable decentralized applications, the introduction of a decentralized cost model around Ethereum Gas fees. This new model proposes state-less parallelized execution and verification models while taking advantage of the security offered by the Bitcoin protocol. We may also refer to this as Web 3.0.

@@

Put in context, even Lightning Networks for transactional counts qualifies as a form of sublinear scaling on a transactional basis but not per user, as users must enter the main chain first before entering a payment channel. It requires the state of the blockchain to include users joining the system. This state (ie, UTXO balances) is the primary  factor of efficiency degradation in Bitcoin. Users need to first start on the main chain and then move into the payment channel system to receive money, meaning that scale is at best O(N) where N is the number of users. There are some solutions to this problem of state storage on Bitcoin by reducing it via an alternative accumulator strategy to the cost of increased bandwidth \cite{Dry19}. This approach would make the chain state-less, however validation costs would remain linear to the number of transactions being done. When combined with payment channels, only costs to get in/out are factored into the validation. This offers an interesting design for payments themselves while providing for on-chain availability. We consider this as a satisfactory path for futuristic scalable payments. Hence, it is not possible to employ that strategy with general computations. With this design, we are still left with the issue on how to do general computations at higher efficiency.

@@

While many compelling arguments can be made migrating to a state-less design \cite{Hot19}, it is not possible to achieve sublinear efficiency without sacrificing some other desired component as outlined above. To achieve polylogarithmic efficiency, it is necessary to have a mix of state and stateless nodes working together in harmony on a shared ledger \cite{Hot19}. This should be accomplished so that business processes can dictate direction, and users can choose to pay a little more for security either by using a stateful (yet very scalable ledgering mechanism) or by paying to ensure their own data availability amortized over the life of that user on such systems. Presenting the ability for users to make these choices allows us to separate the consensus of such systems and reduce overall complexity. However, in whatever solution we adopt, we need to ensure that the final implementation allows for both the liveness and safety of that state, which are defined as follows:

@@

Hardware enclaves (eg, Intel SGX through remote attestation) were also of particular interest to the Syscoin team as a way to offload execution and avoid re-execution costs. However, there are a myriad of attack vectors and censorship concerns on the Intel platform. We should also note that the Antarctica model was interesting but required a firmware update from Intel to support such a feature which raises concerns over censorship long term \cite{Nil20}.

The theme amongst all of these approaches is that although re-execution is avoided, the communication complexity is largely still linear with the number of transactions on the main chain. The security and trust models are also different from that of the layer 1 assumptions which was not desired.

@@

ZKP allows for the desired superlinear scaling trait we had been looking to achieve, but also offer other benefits; namely privacy is very easy to introduce and will not add detectable costs and complexities to verification on the mainchain. With users controlling their own data, the mainchain and systems may be designed such that only balance adjustments are recorded, not transaction sets (we will explain the case with full data availability below). In this scenario, there is no advantage for a miner to gain when colluding with users that launch attacks on systems such as Decentralize Finance (DeFi), pools and provenance of transactions. The flexibility has to be present for application developers that need experiences consistent with those we have today with Bitcoin/Syscoin/Ethereum. This would enable the privacy use-cases without requiring extra work, knowledge or costs.

@@

Hashing with the SHA256 algorithm is regarded to be quantum safe because it requires Grover's algorithm to crack in the post-quantum world, and at best a quantum computer will offer only 50\% reduction in time to break \cite{Nai19}. On the other hand, where Shor’s algorithm applies, any pair based cryptographic system will be broken in hours.

@@

\begin{figure}[h!]
\includegraphics[width=3.5in]{img/4_layer.png}
\label{fig:tech_stack}
\caption{Proposed 4-layer tech stack for Syscoin} 
\end{figure}

@@

As seen in Figure 6, work done on BTC is reused to create SYS blocks through the merged-mining specification. Concurrently, the miner will execute smart contracts in the memory pool of the node running the EVM chain. Once a chain hash has been established post-execution, it will be put into a Syscoin block and published to the network. Upon receiving these blocks, every node would verify that the EVM chain, which can be locally executed (ie, similar to the miner), matches the state described by the Syscoin block. Technically, one would want to ensure both the latest and previous EVM block hashes inside of their respective Syscoin blocks are valid. The block $->$ evmblock $==$ evmblock \&\& block $->$ prev $==$ evmblock $->$ prev is all that is needed to link the chains together with work done by Bitcoin which is propagated to Syscoin through AUXPOW and can serve as a secure ledgering mechanism for the EVM chain.

Since (a) we may use eWASM; (b) there are paid full nodes running on the network; and (c) the mining costs are shared with Bitcoin miners, we should be able to safely increase the amount of bandwidth available in the EVM chain while remaining secure from large uncle orphan rates. There has been much discussion as to what the safe block size should be on Ethereum. Gas limits are increasing as optimizations are made on the Ethereum network. However, since this network would be ledgered by the Syscoin chain through PoW, there shouldbe no concern for uncle orphaning of blocks since the blocks must adhere to the policy set inside of the Syscoin block. We should therefore be able to increase bandwidth significantly and parameterize for a system that will scale globally yet still be centered around L2 rollup designs. A very important distinction to note is that the design of Ethereum 2.0 centers around a Beacon chain and sharding served by a Casper consensus algorithm \cite{But17}. The needs of the algorithm require a set of finality guarantees necessitating a move towards Proof-of-Stake (PoS). This has large security implications for which we may not have formal analysis for a long time, however we do know it comes with big risk \cite{Neu21}.  We offer similar levels of scalability on a network while retaining Nakamoto Consensus security. The simpler design which has been market tested and academically verified to work would result in a more efficient system as a whole with less unknown and undocumented attack vectors. Hence, we need only to consider researching the optimal parameterization of the gas limit taking into account an L2 centric system; but also a safe number of users we expect to be able to serve before fee market mechanisms begin to regulate the barrier of entry for these users. This proposed system should be scalable enough to serve the needs of global generalized computation while sticking to the core fundamentals set forth in the design explained above. Our upcoming whitepaper will have more analysis on these numbers but we will include some theoretical scaling metrics at the end of this article.

@@

Aleo uses Zero knowledge EXEcution (Zexe) for zkSNARK proof creation through circuits created from R1CS constraints. The interesting thing about Aleo is that there is a ledger itself that is purpose-built to only verify these Zexe proofs for privacy preserving transactability. The consensus is PoW, while the proof system involves optimizing over the ability to calculate the verifications of these proofs efficiently. The more efficient these miners become at verifying these proofs, the faster they are able to mine and thus the system provides sybil resistance through providing resources to verify Zexe proofs as a service in exchange for block creation. However, these proof creations can be done in parallel based on the business logic for the systems the developers need to create. There is no direct need for on-chain custom verification as these can be done in an EVM contract, similar to what Cairo Generic Proving Service (GPS) verifier and Zinc Verification do. The goal of Aleo is to incentivize miners to create specialized hardware to more efficiently mine blocks with verification proofs. However, provers can also do this as we have seen with Matter Labs’ recent release of FPGA to do more efficient zkSNARK proofs \cite{Glu20}. It is a desirable property to use PoW to achieve “world-view” consensus in Aleo; however they focus on private transactions. They are typically not batched and employ a recursive outer proof to guarantee execution of an inner proof where the outer proof is sent to the blockchain to be verified. This proof is a limited 2-step recursion, consequently batching of arbitrary amounts of transactions is not supported. As a result, the cost of proof verification is relatively constant with a trade-off of limiting the recursion depth. Aleo is not meant to be a scalable aggregator of transactions, but mainly oriented towards privacy in their zk-SNARK constructions using Zexe.

@@

An EVM layer will support general smart contracts compatible with existing Ethereum infrastructure and L2 rollups will enable massive scale. The different types of zkRollups will allow businesses and rollup providers to offer ability for custom fee markets (ie, pay for fees in tokens other than base layer token SYS). In addition, it will remove costs and thus improve scale of systems by offering custom data availability consensus modules. This design here shares similarities to the zkPorter design where a smart contract would sign off on data availability checks that would get put into the ZKP as part of the validity of a zkBlock which goes on chain.

@@

This concludes that shards can define different consensus modules for data availability (censorship resistance mechanisms) via separating concerns around ledgering the world-view of the state (ie, ZKP that is put on L1) and the data that represents the state. Doing so would allow shards to increase scale, offload costs of data availability to consensus participants.

@@

Since payment channels work with UTXO’s and also benefit from on-chain scaling via Z-DAG, 16MB blocks (with segwit weight) assumed, we will see somewhere around 8MB-12MB effectively per minute (per block). We foresee that is sufficient to serve Seven Billion people who may enter and exit the payment channel networks once a year (ie, 2 transactions on chain per person per year) for a total of 14 Billion transactions. Let’s conservatively assume 8MB blocks and 300 bytes per transaction. Once on a payment channel, the number of transactions is not limited to on-chain bandwidth, but to network related latencies and bandwidth costs. Therefore, we will conclude that our payment scalability will be able to serve billions of people doing 2 on-chain transactions per year which is arguably realistic based on the way we envision payments to unfold; whether that is an L2 or payment channel network that will hold users to pay through instant transaction mechanisms. On-chain, we have some metrics on Z-DAG throughput [1]; in those cases someone needs to transact for point-of-sale using the Syscoin chain. The solution for payments ends up looking like a hybrid mechanism of on-chain (ie, Z-DAG) and off-chain (ie, payment channel) style payments.

@@

\subsubsection{Gas Costs and Block Sizing}

Starkware was able to process 300k transactions over 8 blocks with a total cost of 94.5M gas; final throughput was 3000 TPS (see Reddit bake-off estimates). For the following calculations, let’s assume one batch-run to be 300k transactions. Ethereum can process ~200kB of data per minute, with a cost limit of 50M gas per minute. Therefore, considering the Starkware benchmark test, and assuming a block interval of 13 seconds, we would achieve ~ 3000 TPS (ie,  300 k transactions per batch-run / (8 blocks per batch-run * 13 seconds per block))

@@

With regards to the SYSX cost estimates, simulated gas costs were generated using Ethereum's proposed EIP-1559 (Figure \ref{fig:sysx_gas_costs_eip_1559}) and an alternative pricing mechanism that Syscoin is currently exploring (Figure \ref{fig:sysx_gas_costs_m1}). This alternative approach is called the BLock Occupancy Cost (BLOC) function (\ref{fig:bloc}), and is driven by the occupancy of the previously generated block; see Figure \ref{fig:blk_occupancy_simulations} for simulations Appendix D for details.

@@

\section{EIP-1559}
